### 2022-06-29 sections/simulated_samples.tex
revised to V2.1

An overview of the Monte Carlo (MC) generators used for the main signal and background samples is summarized in Table~\ref{mob}.
Samples of simulated $\ttbar \to WbHq$ ($tt(qH)$) events were generated with the next-to-leading order (NLO) generator\footnote{In the following, 
the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix-element (ME) calculation 
is performed.} {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
%{\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
with the NNPDF3.0 NLO~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} with the NNPDF2.3 LO~\cite{Ball:2012cx} PDF set for the modelling of parton showering (PS), hadronisation, and the underlying event. 
The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
initial- and final-state radiation, referred to as the tune, was used.
The signal sample is normalised to the same total cross section as is used for the inclusive $t\bar{t}\to WbWb$ sample (see discussion below)
assuming a benchmark branching ratio of $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$.
The case of both top quarks decaying into $qH$ is neglected in the analysis given the existing upper limits on $\BR(t \to qH)$ (Section~\ref{sec:intro}).

The $tH$ signal events were generated by {\amcatnlolong}~2.6.2~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
with the NNPDF3.0 NLO parton distribution function (PDF) set. The parton showers, hadronisation, and underlying event are modelled by {\pythia}~8.212 with the NNPDF2.3 LO PDF set
in combination with the A14 tune.
%and interfaced to {\pythia} 8.212 with the NNPDF2.3 LO PDF set for the modelling of parton showering,
%hadronisation, and the underlying event with the A14 tune.
Depending on whether the up quark or the charm quark is involved in the FCNC production, the effective Lagrangian of the $tqH$ interaction is parametrised using
dimension-6 operators~\cite{fcnc_production_theory}. We obtain $\sigma(ug\to tH)$ = 0.711 pb and $\sigma(cg\to tH)$ = 0.103 pb using $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$ as the benchmark.

The sample used to model the $\ttbar$ background was generated with the NLO generator {\powheg}~v2
%\cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
using the NNPDF3.0 NLO PDF set. The {\powheg} model parameter $h_{\textrm{damp}}$, which controls 
matrix element to parton shower matching and regulates the high-$\pt$ radiation, was set to 1.5 times the top-quark mass. 
The parton showers, hadronisation, and underlying event were modelled by {\pythia}~8.210 with the NNPDF2.3 LO PDF set in combination with the A14 tune.
Alternative $\ttbar$ simulation samples used to derive parton shower systematic uncertainties are described in Section~\ref{sec:syst_bkgmodeling}. 
The generated $\ttbar$ samples are normalised to a theoretical cross section of $832^{+46}_{-51}$~pb, 
computed using \textsc{Top++}~v2.0~\cite{Czakon:2011xx} at next-to-next-to-leading order (NNLO), 
including resummation of next-to-next-to-leading logarithmic (NNLL) soft gluon 
terms~\cite{Cacciari:2011hy,Baernreuther:2012ws,Czakon:2012zr,Czakon:2012pz,Czakon:2013goa}.

Samples of single-top-quark events corresponding to the $t$-channel production mechanism were generated with a  
{\powheg}~v2 generator~\cite{Frederix:2012dh}, using the 4F scheme  for the NLO matrix-element calculations
and the corresponding NNPDF3.0 NLO set of PDFs.
Samples corresponding to the $tW$- and $s$-channel production mechanisms were generated 
with {\powheg}~v2 using the five-flavour scheme. Overlaps between the $\ttbar$ and $tW$ final states were avoided by using 
the diagram removal scheme~\cite{Frixione:2005vw}.
The parton showers, hadronisation and underlying event were modelled using {\pythia}~8.230~\cite{Sjostrand:2006za} using the A14 tune and the NNPDF2.3 LO PDF set.
%with the CTEQ6L1~\cite{Pumplin:2002vw,Nadolsky:2008zw} PDF set %in combination with the Perugia 2012 tune~\cite{Skands:2010ak}.
The single-top-quark samples are normalised to the approximate NNLO theoretical cross 
sections~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.

Samples of $W/Z$+jets events were generated with the {\sherpa}~2.2.1~\cite{Gleisberg:2008ta} generator. 
The matrix element was calculated for up to two partons at NLO and up to four partons at LO using 
\textsc{Comix}~\cite{Gleisberg:2008fv} and \textsc{OpenLoops}~\cite{Cascioli:2011va}. The matrix-element calculation 
is merged with the {\sherpa} parton shower~\cite{Schumann:2007mg} using the ME+PS@NLO prescription~\cite{Hoeche:2012yf}. 
The PDF set used for the matrix-element calculation is NNPDF3.0 NNLO~\cite{Ball:2014uwa} with a dedicated parton shower tuning developed for {\sherpa}. 
Separate samples were generated for different $W/Z$+jets categories using filters for a $b$-jet 
($W/Z$+$\geq$1$b$+jets), a $c$-jet and no $b$-jet ($W/Z$+$\geq$1$c$+jets), and with a veto on $b$- and $c$-jets 
($W/Z$+light-jets), which are combined into the inclusive $W/Z$+jets samples.
Both the $W$+jets and $Z$+jets samples are normalised to their respective inclusive NNLO theoretical 
cross sections calculated with \textsc{FEWZ}~\cite{Anastasiou:2003ds}.

Samples of $WW/WZ/ZZ$+jets events were generated with {\sherpa}~2.2.1 using the CT10 PDF set
and include processes containing up to four electroweak vertices. 
In the case of $WW/WZ$+jets ($ZZ$+jets) the matrix element was calculated for zero (up to one) additional partons 
at NLO and up to three partons at LO using the same procedure as for the $W/Z$+jets samples. 
The final states that were simulated require one of the bosons to decay leptonically and the other hadronically.
All diboson samples are normalised to their NLO theoretical cross sections provided by {\sherpa}.

Samples of $\ttbar V$ ($V=W\, Z$ boson) and $\ttbar H$ events were generated with {\amcatnlo}~2.2.1, using NLO matrix elements and the NNPDF3.0 NLO PDF set,
and interfaced to {\pythia}~8.210 with the NNPDF2.3 LO PDF set and the A14 tune. 
%Instead, the $\ttbar V$ samples used in the $\Hbb$ search are based on LO matrix elements computed for up to two additional partons 
%using the NNPDF3.0 NLO PDF set, and merged using the CKKW-L approach~\cite{Lonnblad:2001iq}.
The $\ttbar V$ samples are normalised to the NLO cross section computed with {\amcatnlo}, while the $\ttbar H$ sample is normalised using 
the NLO cross section recommended in Ref.~\cite{deFlorian:2016spz}.

Samples of $WH$ and $ZH$, collectively referred to as $VH$, are generated using {\powheg}~v2\cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
and interfaced to {\pythia}~8.210 with the PDF4LHC15 PDF set and the AZNLO tune.
The contribution of $tH$ associated production is also considered as part of the SM Higgs background.
The sample is generated using {\amcatnlolong}~2.6.2~\cite{Alwall:2014hca} and interfaced with {\pythia}~8.210 with CT10PDF
and the A14 tune. The MC predictions are normalised using the NLO cross section recommended in Ref.~\cite{deFlorian:2016spz}.
The contribution of triboson production is found to be negligible.

All generated samples, except those produced with the {\sherpa}~\cite{Gleisberg:2008ta} event generator, 
utilise \textsc{EvtGen}~1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
%To model the effects of pile-up, events from minimum-bias interactions were generated using {\pythia}~8.186~\cite{Sjostrand:2007gs}  
%in combination with the A3 tune~\cite{ATL-PHYS-PUB-2011-014}, 
The effects of multiple interactions in the same and nearby bunch crossings (pile-up) were modelled by overlaying minimum-bias events, simulated using the soft QCD processes of {\pythia}~8.186~\cite{Sjostrand:2006za} with the A3~\cite{ATL-PHYS-PUB-2016-017} set of tuned parameters and NNPDF2.3 LO PDF set~\cite{Ball:2012cx}.
%parton distribution functions (PDF).

@@

\begin{table}
\footnotesize
\centering
\caption{Overview of the MC generators used for the main signal and background samples, including the matrix element (ME), parton shower (PS), parton distribution function set (PDF), and cross-section calculation order (Order).}
\begin{tabular}[h]{l|c|c|c|c|c|c}
\hline \hline
\multirow{2}{*}{Process} & \multicolumn{2}{c|}{Generator} & \multicolumn{2}{c|}{PDF set} & \multirow{2}{*}{Tune} & \multirow{2}{*}{Order} \\ \cline{2-5}
        &  ME   &  PS    &  ME  & PS &   &  \\\hline
$tt(qH)$ Signal & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$tH$ Signal & {\amcatnlolong} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$W/Z$+jets & \multicolumn{2}{c|}{{\sherpa}~2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & {\sherpa} & NLO/LO \\ \hline
\ttbar & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
Single top & {\powheg} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$t\bar{t}X$ & {\amcatnlolong} & {\pythia}~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$VH$ & {\powheg} & {\pythia}~8 & PDF4LHC15&CTEQ6L1 & AZNLO & NLO \\ \hline
$tH$ & {\amcatnlolong} & {\pythia}~8 & \multicolumn{2}{c|}{CT10PDF} & A14 & NLO \\ \hline
Diboson & \multicolumn{2}{c|}{{\sherpa}~2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & {\sherpa} & NLO/LO \\ \hline\hline
\end{tabular}
\label{mob}
\end{table}

>>>>

An overview of the Monte Carlo (MC) generators used for the main signal and background samples is summarised in Table~\ref{mob}.
Samples of simulated $\ttbar \to WbHq$ ($tt(qH)$) events were generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix-element (ME) calculation 
is performed.} {\powheg}\,v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
%{\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
with the \textsc{NNPDF3.0nlo}~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia}\,8.212~\cite{Sjostrand:2007gs} with the \textsc{NNPDF2.3lo}~\cite{Ball:2012cx} PDF set for the modelling of the parton showers (PS), hadronisation, and underlying event. 
A set of tuned parameters called the A14 tune~\cite{ATLASUETune4} was used in {\pythia} to control the modelling of multi-parton interactions and  
initial- and final-state radiation.
The signal sample is normalised to the same total cross section as is used for the inclusive $t\bar{t}\to WbWb$ sample (see discussion below)
assuming a benchmark branching ratio of $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$.
The case of both top quarks decaying into $qH$ is neglected in the analysis given the existing upper limits on $\BR(t \to qH)$ (Section~\ref{sec:intro}).

The $tH$ signal events were generated by {\amcatnlolong}\,2.6.2~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
with the \textsc{NNPDF3.0nlo} parton distribution function (PDF) set. The parton showers, hadronisation, and underlying event were modelled by {\pythia}\,8.212 with the \textsc{NNPDF2.3lo} PDF set
in combination with the A14 tune.
%and interfaced to {\pythia} 8.212 with the NNPDF2.3 LO PDF set for the modelling of parton showering,
%hadronisation, and the underlying event with the A14 tune.
Depending on whether the up quark or the charm quark is involved in the FCNC production process, the effective Lagrangian of the $tqH$ interaction is parameterised using
dimension-6 operators~\cite{fcnc_production_theory}. The cross sections $\sigma(ug\to tH) = 0.711$~pb and $\sigma(cg\to tH) = 0.103$~pb were obtained using $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$ as the benchmark.

The sample used to model the $\ttbar$ background was generated with the NLO generator {\powheg}\,v2
%\cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
using the \textsc{NNPDF3.0nlo} PDF set. The {\powheg} model parameter $h_{\textrm{damp}}$, which controls 
matrix element to parton shower matching and regulates the high-$\pt$ radiation, was set to 1.5 times the top-quark mass. 
The parton showers, hadronisation, and underlying event were modelled by {\pythia}\,8.210 with the \textsc{NNPDF2.3lo} PDF set in combination with the A14 tune.
Alternative $\ttbar$ simulation samples used to derive parton shower systematic uncertainties are described in Section~\ref{sec:syst_bkgmodeling}. 
The generated $\ttbar$ samples are normalised to a theoretical cross section of $\sigma_{\ttbar}=832^{+46}_{-51}$~pb, 
computed using \textsc{Top++}\,2.0~\cite{Czakon:2011xx} at next-to-next-to-leading order (NNLO), 
including resummation of next-to-next-to-leading logarithmic (NNLL) soft gluon 
terms~\cite{Cacciari:2011hy,Baernreuther:2012ws,Czakon:2012zr,Czakon:2012pz,Czakon:2013goa}.

Samples of single-top-quark events corresponding to the $t$-channel production mechanism were generated with the  
{\powheg}\,v2 generator~\cite{Frederix:2012dh}, using the four-flavour scheme  for the NLO matrix-element calculations
and the corresponding \textsc{NNPDF3.0nlo} set of PDFs.
Samples corresponding to the $tW$- and $s$-channel production mechanisms were generated 
with {\powheg}\,v2 using the five-flavour scheme. Overlaps between the $\ttbar$ and $tW$ final states were avoided by using 
the diagram removal scheme~\cite{Frixione:2005vw}.
The parton showers, hadronisation and underlying event were modelled using {\pythia}\,8.230~\cite{Sjostrand:2006za} with the A14 tune and the \textsc{NNPDF2.3lo} PDF set.
%with the CTEQ6L1~\cite{Pumplin:2002vw,Nadolsky:2008zw} PDF set %in combination with the Perugia 2012 tune~\cite{Skands:2010ak}.
The single-top-quark samples are normalised to the approximate NNLO theoretical cross 
sections~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.

Samples of $W/Z$+jets events were generated with the {\sherpa}\,2.2.1~\cite{Gleisberg:2008ta} generator. 
The matrix element was calculated for up to two partons at NLO and up to four partons at LO using 
\textsc{Comix}~\cite{Gleisberg:2008fv} and \textsc{OpenLoops}~\cite{Cascioli:2011va}. The matrix-element calculation 
was merged with the {\sherpa} parton shower~\cite{Schumann:2007mg} using the MEPS@NLO prescription~\cite{Hoeche:2012yf}. 
The PDF set used for the matrix-element calculation is \textsc{NNPDF3.0nnlo}~\cite{Ball:2014uwa} with a dedicated parton shower tune developed for {\sherpa}. 
Separate samples were generated for different $W/Z$+jets categories using filters for a $b$-jet 
($W/Z$+$\geq$1$b$+jets), a $c$-jet and no $b$-jet ($W/Z$+$\geq$1$c$+jets), and with a veto on $b$- and $c$-jets 
($W/Z$+light-jets), and were combined into the inclusive $W/Z$+jets samples.
The $W$+jets and $Z$+jets samples are normalised to their respective inclusive NNLO theoretical 
cross sections calculated with \textsc{FEWZ}~\cite{Anastasiou:2003ds}.

Samples of $WW/WZ/ZZ$+jets events were generated with {\sherpa}\,2.2.1 using the CT10 PDF set
and include processes containing up to four electroweak vertices. 
In the case of $WW/WZ$+jets ($ZZ$+jets) the matrix element was calculated for zero (up to one) additional partons 
at NLO and up to three partons at LO using the same procedure as for the $W/Z$+jets samples. 
The final states that were simulated require one of the bosons to decay leptonically and the other hadronically.
All diboson samples are normalised to their NLO theoretical cross sections provided by {\sherpa}.

Samples of $\ttbar V$ ($V=W, Z$ boson) and $\ttbar H$ events were generated with {\amcatnlo}\,2.2.1, using NLO matrix elements and the \textsc{NNPDF3.0nlo} PDF set,
and interfaced to {\pythia}\,8.210 with the \textsc{NNPDF2.3lo} PDF set and the A14 tune. 
%Instead, the $\ttbar V$ samples used in the $\Hbb$ search are based on LO matrix elements computed for up to two additional partons 
%using the NNPDF3.0 NLO PDF set, and merged using the CKKW-L approach~\cite{Lonnblad:2001iq}.
The $\ttbar V$ samples are normalised to the NLO cross section computed with {\amcatnlo}, while the $\ttbar H$ sample is normalised using 
the NLO cross section recommended in Ref.~\cite{deFlorian:2016spz}.

Samples of $WH$ and $ZH$, collectively referred to as $VH$, were generated using {\powheg}\,v2~\cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
and interfaced to {\pythia}\,8.210 with the PDF4LHC15 PDF set and the AZNLO tune.
The contribution of $tH$ associated production is also considered as part of the SM Higgs background.
The sample was generated using {\amcatnlolong}\,2.6.2~\cite{Alwall:2014hca} and interfaced to {\pythia}\,8.210 with the CT10 PDF set
and the A14 tune. The MC predictions are normalised using the NLO cross section recommended in Ref.~\cite{deFlorian:2016spz}.
The contribution of triboson production is found to be negligible.

All generated samples, except those produced with the {\sherpa}~\cite{Gleisberg:2008ta} event generator, 
utilise \textsc{EvtGen}\,1.2.0~\cite{Lange:2001uf} to model the decays of heavy-flavour hadrons. 
%To model the effects of pile-up, events from minimum-bias interactions were generated using {\pythia}~8.186~\cite{Sjostrand:2007gs}  
%in combination with the A3 tune~\cite{ATL-PHYS-PUB-2011-014}, 
The effects of multiple interactions in the same and nearby bunch crossings (pile-up) were modelled by overlaying minimum-bias events, simulated using the soft QCD processes of {\pythia}\,8.186~\cite{Sjostrand:2006za} with the A3 tune~\cite{ATL-PHYS-PUB-2016-017} and \textsc{NNPDF2.3lo} PDF set~\cite{Ball:2012cx}.
%parton distribution functions (PDF).

@@

\begin{table}
\footnotesize
%\centering
\caption{Overview of the MC generators used for the main signal and background samples, including the matrix element (ME), parton shower (PS), parton distribution function set (PDF), and cross-section calculation order (Order).}
\begin{center}
\begin{tabular}[h]{l|c|c|c|c|c|c}
\hline \hline
\multirow{2}{*}{Process} & \multicolumn{2}{c|}{Generator} & \multicolumn{2}{c|}{PDF set} & \multirow{2}{*}{Tune} & \multirow{2}{*}{Order} \\ \cline{2-5}
        &  ME   &  PS    &  ME  & PS &   &  \\\hline
$tt(qH)$ signal & {\powheg} & {\pythia}\,8 & \textsc{NNPDF3.0nlo} & \textsc{NNPDF2.3lo} & A14 & NLO \\ \hline
$tH$ signal & {\amcatnlolong} & {\pythia}~8 & \textsc{NNPDF3.0nlo} & \textsc{NNPDF2.3lo} & A14 & NLO \\ \hline
$W/Z$+jets & \multicolumn{2}{c|}{{\sherpa}\,2.2.1} & \multicolumn{2}{c|}{\textsc{NNPDF3.0nnlo}} & {\sherpa} & NLO/LO \\ \hline
\ttbar & {\powheg} & {\pythia}\,8 & \textsc{NNPDF3.0nlo} & \textsc{NNPDF2.3lo} & A14 & NLO \\ \hline
Single top & {\powheg} & {\pythia}\,8 & \textsc{NNPDF3.0nlo} & \textsc{NNPDF2.3lo} & A14 & NLO \\ \hline
$t\bar{t}X$ & {\amcatnlolong} & {\pythia}\,8 & \textsc{NNPDF3.0nlo} & \textsc{NNPDF2.3lo} & A14 & NLO \\ \hline
$VH$ & {\powheg} & {\pythia}\,8 & PDF4LHC15&CTEQ6L1 & AZNLO & NLO \\ \hline
$tH$ & {\amcatnlolong} & {\pythia}\,8 & \multicolumn{2}{c|}{CT10} & A14 & NLO \\ \hline
Diboson & \multicolumn{2}{c|}{{\sherpa}\,2.2.1} & \multicolumn{2}{c|}{\textsc{NNPDF3.0nnlo}} & {\sherpa} & NLO/LO \\ \hline\hline
\end{tabular}
\end{center}
\label{mob}
\end{table}

### 2022-06-29 sections/statistical_analysis.tex
revised to V2.1

The final discriminant distributions are the BDT outputs of all the considered analysis regions. They are jointly analysed for the 
presence of a signal. The BDT distributions are binned to maximize sensitivity to the signal.
The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
a product of Poisson probability terms over all bins considered in the search. This function depends
on the signal-strength parameter $\mu$, defined as a factor multiplying the expected yield of $tH$ and $tt(qH)$ signal events
normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$;
and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties on the signal and background expectations.
The $pp\rightarrow tH$ production cross section is related to $\BR(t\rightarrow qH)$ through their dimension-6 operators~\cite{fcnc_production_theory}.
It follows that the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
All nuisance parameters are subject to Gaussian constraints on the likelihood.
For a given value of $\mu$, the nuisance parameters $\theta$ allow variations of the expectations for signal and background
consistent with the corresponding systematic uncertainties, and their fitted values result in the deviations from
the nominal expectations that globally provide the best fit to the data.
This procedure allows a reduction of the impact of systematic uncertainties on 
the search's sensitivity by taking advantage of the highly populated background-dominated bins included in the likelihood fit.
%To verify the improved background prediction, fits under the background-only hypothesis are performed, 
%and differences between the data and the post-fit background prediction are checked 
%using kinematic variables other than the ones used in the fit. 
Statistical uncertainties in each bin of the predicted final discriminant distributions are taken into account through dedicated parameters in the fit.     
The best-fit $\BR(t\to qH)$ is obtained by performing a binned likelihood fit to the data under the signal-plus-background
hypothesis, and maximising the likelihood function ${\cal L}(\mu,\theta)$ over $\mu$ and $\theta$.

The fitting procedure was initially validated through extensive studies using pseudodata (which is defined as the sum of all predicted backgrounds 
plus an injected signal of variable strength) as well as by performing fits to real data where bins of the final discriminant variable with 
a signal contamination above 10\% are excluded (referred to as blinding requirements).
In both cases, the robustness of the model for systematic uncertainties is established by verifying the stability of the fitted background 
when varying assumptions about some of the leading sources of uncertainty. 
After this, the blinding requirements
are removed in the data and a fit under the signal-plus-background hypothesis is performed. Further checks involve the comparison of the fitted 
nuisance parameters before and after removal of the blinding requirements, and their values are found to be consistent. In addition, it is verified that the 
fit is able to determine the strength of a simulated signal injected into the real data.

The test statistic $q_\mu$ is defined as the profile likelihood ratio, 
$q_\mu = -2\ln({\cal L}(\mu,{\hat{\theta}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$,
where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that
maximise the likelihood function (subject to the constraint $0\leq \hat{\mu} \leq \mu$), and the ${\hat{\theta}}_\mu$ are the values of the
nuisance parameters that maximise the likelihood function for a given value of $\mu$. 
The test statistic $q_\mu$ is evaluated with the {\textsc RooFit} package~\cite{Verkerke:2003ir,RooFitManual}.
%A related statistic is used to determine whether the observed data is compatible with the background-only hypothesis (the so-called discovery test)  
%by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
%The $p$-value (referred to as $p_0$), representing the level of agreement between the data and the background-only hypothesis, is estimated by integrating
%%representing the probability of the data being compatible with the background-only hypothesis is estimated by integrating
%%the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
%the distribution of $q_0$ based on the asymptotic formulae in Ref.~\cite{Cowan:2010js}, 
%above the observed value of $q_0$ in the data. 
%%The observed $p_0$-value is checked for each explored signal scenario.
%%In the case of the data being compatible with the background-only hypothesis, 
%Upper limits on $\mu$, and thus on 
%$\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
%For a given signal scenario, values of the $\BR(t\to Hq)$ yielding CL$_{\textrm{s}} < 0.05$, 
%where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.

%In the absence of signal,
Exclusion limits are set on $\mu$ and thus on
$\BR(t\to qH)$, derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
For a given signal scenario, values of the $\BR(t\to qH)$ yielding CL$_{\textrm{s}} < 0.05$,
where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.

>>>>

The final discriminant distributions are the BDT outputs from all the considered analysis regions. They are jointly analysed for the 
presence of a signal. The BDT distributions are binned to maximise sensitivity to the signal.
The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
a product of Poisson probability terms over all bins considered in the search. This function depends
on the signal-strength parameter $\mu$, defined as a factor multiplying the expected yield of $tH$ and $tt(qH)$ signal events
normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to qH)=0.1\%$,
and on $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties on the signal and background expectations.
The $pp\rightarrow tH$ production cross section is related to $\BR(t\rightarrow qH)$ through their dimension-6 operators~\cite{fcnc_production_theory}.
It follows that the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
All nuisance parameters are subject to Gaussian constraints in the likelihood function.
For a given value of $\mu$, the nuisance parameters $\theta$ allow variations of the expectations for signal and background
consistent with the corresponding systematic uncertainties, and their fitted values result in the deviations from
the nominal expectations that globally provide the best fit to the data.
This procedure reduces the impact of systematic uncertainties on 
the search's sensitivity by taking advantage of the highly populated background-dominated bins included in the likelihood fit.
%To verify the improved background prediction, fits under the background-only hypothesis are performed, 
%and differences between the data and the post-fit background prediction are checked 
%using kinematic variables other than the ones used in the fit. 
Statistical uncertainties in each bin of the predicted final discriminant distributions are taken into account through dedicated parameters in the fit.     
The best-fit $\BR(t\to qH)$ is obtained by performing a binned likelihood fit to the data under the signal-plus-background
hypothesis, and maximising the likelihood function ${\cal L}(\mu,\theta)$ over $\mu$ and $\theta$.

The fitting procedure was initially validated through extensive studies using pseudo-data (which is defined as the sum of all predicted backgrounds 
plus an injected signal of variable strength) as well as by performing fits to real data where bins of the final discriminating variable with 
a signal contamination above 10\% are excluded (referred to as `blinding' requirements).
In both cases, the robustness of the model with respect to systematic uncertainties is established by verifying the stability of the fitted background 
when varying assumptions about some of the leading sources of uncertainty. 
After this, the blinding requirements
are removed in the data and a fit under the signal-plus-background hypothesis is performed. Further checks involve the comparison of the fitted 
nuisance parameters before and after removal of the blinding requirements, and their values are found to be consistent. In addition, it is verified that the 
fit is able to determine the strength of a simulated signal injected into the real data.

The test statistic $q_\mu$ is defined as the profile likelihood ratio, 
$q_\mu = -2\ln({\cal L}(\mu,{\hat{\hat{\theta}}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$,
where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that
maximise the likelihood function (subject to the constraint $0\leq \hat{\mu} \leq \mu$), and the ${\hat{\hat{\theta}}}_\mu$ are the values of the
nuisance parameters that maximise the likelihood function for a given value of $\mu$. 
The test statistic $q_\mu$ is evaluated with the {\textsc RooFit} package~\cite{Verkerke:2003ir,RooFitManual}.
%A related statistic is used to determine whether the observed data is compatible with the background-only hypothesis (the so-called discovery test)  
%by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
%The $p$-value (referred to as $p_0$), representing the level of agreement between the data and the background-only hypothesis, is estimated by integrating
%%representing the probability of the data being compatible with the background-only hypothesis is estimated by integrating
%%the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
%the distribution of $q_0$ based on the asymptotic formulae in Ref.~\cite{Cowan:2010js}, 
%above the observed value of $q_0$ in the data. 
%%The observed $p_0$-value is checked for each explored signal scenario.
%%In the case of the data being compatible with the background-only hypothesis, 
%Upper limits on $\mu$, and thus on 
%$\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
%For a given signal scenario, values of the $\BR(t\to Hq)$ yielding CL$_{\textrm{s}} < 0.05$, 
%where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.

%In the absence of signal,
Exclusion limits are set on $\mu$ and thus on
$\BR(t\to qH)$, derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
For a given signal scenario, values of $\BR(t\to qH)$ yielding CL$_{\textrm{s}} < 0.05$,
where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded with at least 95\% confidence.
